---
title: "Untitled"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
---

```{r setup, include=FALSE}
library(flexdashboard)
```

rows {data-width=650}
-----------------------------------------------------------------------

### Twitter Count

```{r}
library(gplots)
library(tm)
library(wordcloud)
library(stringr)
library(flexdashboard)
library(SnowballC)
library(dplyr)
library(reshape2)
library(ggplot2)
library(base)
library(plotly)

setwd("D:\\dataVisualization")
Twitter<-read.csv("narendramodi_tweets.csv",header = TRUE)

TweetsCount<-length(unique(Twitter$text)) 
valueBox(TweetsCount,icon = "fa-pencil",color ="Red")
```

### Average Retweets

```{r}

AverageRetweets<-round(mean(Twitter$retweets_count),digits = 2) 
valueBox(AverageRetweets,icon = "fa fa-coffee")
```

### Average Favorites

```{r}
AverageFavorites<-round(mean(Twitter$favorite_count),digits = 2) 
valueBox(AverageFavorites,icon = "fa fa-coffee")
```

rows {data-width=350}
-----------------------------------------------------------------------

### Top 5 Words

```{r}

Twitter$date<-as.Date(Twitter$created_at,'%Y-%m-%d %H:%M:%S')
Twitter$Quarters<-quarters(Twitter$date)
Twitter$text<-as.character(Twitter$text)
words<-strsplit(Twitter$text,' ')
words_list<-unlist(words)
wordtable<-table(words_list)
wordtable<-sort(wordtable,decreasing = TRUE)
wordframe<-as.data.frame(wordtable)
stop_words<-stopwords()
custom_stop_words<-c("&amp;","rt","рд.ре???")
wordframe$words_list<-tolower(wordframe$words_list)
wordframe<-wordframe[!wordframe$words_list %in% stop_words,]
wordframe<-wordframe[!wordframe$words_list %in% custom_stop_words,]
Top5<-head(wordframe,5)
Topwords<-Top5$words_list
for (word in Topwords){
Twitter[word]<-str_count(Twitter$text,word)
}
abc<-select(Twitter,Quarters,will,india,people,pm)
meltdata<-melt(abc,id.vars ="Quarters")
trans<-meltdata %>% group_by(Quarters,variable) %>% summarise(count=sum(value))
ggplot(trans,aes(x=Quarters,y=count))+geom_bar(stat = "identity",fill='blue')+facet_wrap(~variable)+xlim("Q1","Q2","Q3","Q4")

```

rows {data-width=350}
-----------------------------------------------------------------------

### Top 5 Hashtags 

```{r}

HashNew<-words_list[grepl("#",words_list)]

HashNew=str_replace_all(HashNew,"[[:punct:]]","")

HashNew1<-paste("#",HashNew,sep="")
TopwordsTable<-table(HashNew1)
Topwords<-sort(TopwordsTable,decreasing = TRUE)
Topwordsdf<-as.data.frame(Topwords)
TopHashwords<-head(Topwordsdf,5)
Hashnames<-TopHashwords$HashNew1
  
for (Hashtag in Hashnames) {
  Twitter[Hashtag]<-str_count(Twitter$text,Hashtag)
}
Twitter$Year_month<-format(Twitter$date,'%Y-%m')
WordsData<-filter(Twitter,Year_month>='2016-01' & Year_month <='2016-12')
Hashselect<-select(WordsData,`#Sandesh2Soldiers`,`#MannKiBaat`,`#TirangaYatra`,`#TransformingIndia`,`#YogaDay`,Year_month)
Hashmelt<-melt(Hashselect,id.vars = 'Year_month')
Hashtagyear<-Hashmelt %>% group_by(Year_month,variable) %>% summarise(count=sum(value))
ggplot(Hashtagyear,aes(x=Year_month,y=count,group=variable,color=variable))+geom_line()
```

rows {data-width=350}
-----------------------------------------------------------------------

### Word Cloud representing top 50 words

```{r}
TopHash50<-head(Topwordsdf,50)
library(wordcloud)
wordcloud(TopHash50$HashNew1,TopHash50$Freq,scale=c(2,0.5),colors = brewer.pal(6,'Dark2'))
```

rows {data-width=350}
-----------------------------------------------------------------------

### Visual Story

```{r}
options(scipen = 2)
Twitter2016<-filter(Twitter,Year_month>='2016-01' & Year_month <='2016-12')
Tweets<-Twitter2016%>%group_by(Quarters)%>%summarise(TotalRetweets=sum(retweets_count),TotalFavorites=sum(favorite_count))
ggplot(Tweets,aes(x=Quarters,y=TotalRetweets,fill=TotalFavorites))+ geom_bar(stat = "identity")

```

rows {data-width=150}
-----------------------------------------------------------------------


* It is seen that during the fourth quarter(october to december) modi's tweets received maximum retweets and favorites as during that time Demonitization and surgical strikes occured"


rows {data-width=350}
-----------------------------------------------------------------------

### Visual Story
```{r}
ggplot(Hashtagyear,aes(x=Year_month,y=count,group=variable,color=variable))+geom_line()

```

rows {data-width=350}
-----------------------------------------------------------------------
### Visual Story Insights

* The most used word by modi in the year 2016 is Sandesh2Soldier  & its been used the maximum during the month of october when surgical strikes had happened.
* This tweet by modi was to motivate and congratulate the indian soldiers.In the month of june   modi has maximum  tweets as Yoga  day,This is in  order to  * wish and motivate Indians to practice yoga. Tranforming India is highly being used by modi to promoteDigitilization Digitilization")
